---
title: "README"
author: "Jarrett Byrnes"
date: "June 1, 2015"
output: md_document
---
## A library to work with Spalding et al.'s Marine Ecoregions of the world

This library was developed as I used the MEOW spatial data more and more and wrote a few general functions. The data are from http://www.marineregions.org/downloads.php downloaded on June 1st 2015. See the original paper at http://www.nature.org/ourinitiatives/regions/northamerica/unitedstates/colorado/scienceandstrategy/marine-ecoregions-of-the-world.pdf

##  Installation
```{r, eval=FALSE}
#install.packages("devtools")
library(devtools)
install_github("meowR", "jebyrnes")
```
```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(meowR)
```
## Plotting the SpatialPolygons

```{r}
library(meowR)
data(regions)
data(provinces)
data(realms)

par(mfrow=c(2,2), mar=c(0,1,2,0))
plot(regions, main="Ecoregion")
plot(provinces, lwd=2, border="red", main="Province")
plot(realms, lwd=2, border="blue", main="Realm")
par(mfrow=c(1,1), mar=c(5, 4, 4, 2) + 0.1)
```

## Using data.frame representations with ggplot2 and external data to make a choropleth plot

Each SpatialPolygonsDataFrame has a parallel dataset where the regional information is in a data frame. These have the same names as the sp objects, but with .df in their object name. These were designed to use with plot or ggplot2.

```{r}
data(provinces.df) 
 
base_province_ggplot <- ggplot(provinces.df) + theme_bw() +
aes(long,lat,group=group) + 
  geom_polygon(fill=NA) +
  geom_path(color="black") +
  coord_equal() 
  
  base_province_ggplot
```

```{r}
data(regions.df)

ndf <- data.frame(Ecoregions = levels(regions.df$ECOREGION), 
Values = runif(length(levels(regions.df$ECOREGION)), 0,100))

makeMEOWmap(ndf, fillColName="Values", regionColName="Ecoregions")
```

## Version numbers

`meowR` uses [semantic versioning][semver]. The version numbering
scheme is `major`.`minor`.`revision`. Unless `major` is 1, the package
should not be considered stable. All releases with the same `major`
versions are compatible. Increases in `minor` represents the addition of
backwards-compatible additions. Increases in `revision` represents either
bug fixes or improvements.


## Contributions

People wanting to contribute are welcome to do so by forking the repository,
and submitting a pull request when their work is done. Please also edit the
`DESCRIPTION` file to add your name to the `Authors` field.

[semver]: http://semver.org/